An open and continuously updated fern tree of life (FTOL)

### 2022-02-03 ms/manuscript.Rmd
Update MS

We dated the tree using treePL [@Smith2012].
We applied a set of `r nrow (plastid_calibration_dates)` calibration points as minimum ages.
Our calibration points are all based on fossils (not secondary calibration points) following a careful literature review.
We used the species identification of each fossil to assign lineage only after consulting the original publication; previous studies [`r eg`, @Testo2016a] have used genus to assign lineage, but this can be problematic as genus concepts may vary between the original publication and current taxonomy [`r eg`, *Kuylisporites*\; @Loiseau2020].

@@

set.seed(123)
# Use the ggtree::`%<+%` operator to map the 
# bootstrap values onto the ggtree object
backbone_plot <- 
	ggtree(phy) %<+% bs_tibble +
	# now we can show BS values using geom_text()
	geom_text(aes(label = bootstrap), hjust = -.25, size = 2.5) +
	# add tip labels
	geom_tiplab(aes(label = label)) +
	# highlight major clades
	geom_hilight(
		data = suborder_labels,
		mapping = aes(
			node = mrca,
			fill = plot_group
		),
		alpha = 0.2,
		align = "right",
		extend = 30,
		gradient.direction = "rt",
		roundrect = TRUE,
		gradient.length.out = 2) +
	scale_fill_manual(values = clade_cols) +
	# label major clades
	geom_cladelab(
		data = suborder_labels,
		mapping = aes(
			node = mrca,
			label = clade_label
		),
		offset = 28,
		align = TRUE,
		extend = 0.3,
		hjust = 0,
		barcolour = "grey20",
		barsize = 2) +
	# Label other groups
	geom_label_repel(
		data = other_clade_labels %>%
			filter(clade_label == "Polypodiidae\n(leptosporangiates)"),
		aes(x = x, y = y, label = clade_label),
		hjust = 0,
		xlim = c(NA, 10),
		ylim = c(13, NA),
		color = "grey20",
		segment.color = "grey20"
	) +
	geom_label_repel(
		data = other_clade_labels %>%
			filter(clade_label == "eupolypods"),
		aes(x = x, y = y, label = clade_label),
		hjust = 0,
		xlim = c(NA, 64),
		ylim = c(32, NA),
		color = "grey20",
		segment.color = "grey20"
	) +
	geom_label_repel(
		data = other_clade_labels %>%
			filter(clade_label == "Polypodiales"),
		aes(x = x, y = y, label = clade_label),
		hjust = 0,
		nudge_x = -25,
		nudge_y = 4,
		color = "grey20",
		segment.color = "grey20"
	) +
	xlim(0, 180) +
	coord_cartesian(clip = "off") +
	theme(legend.position = "none")
```

>>>>

We dated the tree using treePL [@Smith2012].
We applied a set of FIXME calibration points as minimum ages.
Our calibration points are all based on fossils (not secondary calibration points) following a careful literature review.
We used the species identification of each fossil to assign lineage only after consulting the original publication; previous studies [`r eg`, @Testo2016a] have used genus to assign lineage, but this can be problematic as genus concepts may vary between the original publication and current taxonomy [`r eg`, *Kuylisporites*\; @Loiseau2020].

@@

set.seed(123)
# Use the ggtree::`%<+%` operator to map the 
# bootstrap values onto the ggtree object
backbone_plot <- 
	ggtree(phy) %<+% bs_tibble +
	# now we can show BS values using geom_text()
	geom_text(aes(label = bootstrap), hjust = -.25, size = 2.5) +
	# add tip labels
	geom_tiplab(aes(label = label)) +
	# highlight major clades
	geom_hilight(
		data = suborder_labels,
		mapping = aes(
			node = mrca,
			fill = plot_group
		),
		alpha = 0.2,
		align = "right",
		extend = 30,
		gradient.direction = "rt",
		roundrect = TRUE,
		gradient.length.out = 2) +
	scale_fill_manual(values = clade_cols) +
	# label major clades
	geom_cladelab(
		data = suborder_labels,
		mapping = aes(
			node = mrca,
			label = clade_label
		),
		offset = 28,
		align = TRUE,
		extend = 0.3,
		hjust = 0,
		barcolour = "grey20",
		barsize = 2) +
	# Label other groups
	geom_text_repel(
		data = other_clade_labels %>%
			filter(clade_label == "Polypodiidae\n(leptosporangiates)"),
		aes(x = x, y = y, label = clade_label),
		hjust = 0,
		xlim = c(NA, 10),
		ylim = c(15, NA),
		color = "grey20",
		segment.color = "grey20"
	) +
	geom_text_repel(
		data = other_clade_labels %>%
			filter(clade_label == "eupolypods"),
		aes(x = x, y = y, label = clade_label),
		hjust = 0,
		xlim = c(NA, 64),
		ylim = c(32, NA),
		color = "grey20",
		segment.color = "grey20"
	) +
	geom_text_repel(
		data = other_clade_labels %>%
			filter(clade_label == "Polypodiales"),
		aes(x = x, y = y, label = clade_label),
		hjust = 0,
		xlim = c(NA, 48),
		ylim = c(24, NA),
		color = "grey20",
		segment.color = "grey20"
	) +
	xlim(0, 180) +
	coord_cartesian(clip = "off") +
	theme(legend.position = "none")
```
